---
title: "HW3"
author: "Shariq Mian"
date: "9/12/2021"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(dplyr)
library(stringr)
library(htmltools)
```

Week 3 assignment
Please deliver links to an R Markdown file (in GitHub and rpubs.com) with solutions to the problems below.  You may work in a small group, but please submit separately with names of all group participants in your submission.

# 1 Using the 173 majors listed in fivethirtyeight.com’s College Majors dataset [https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/], provide code that identifies the majors that contain either "DATA" or "STATISTICS"

```{r load data}
df = read.csv(url('https://github.com/fivethirtyeight/data/raw/e48bfdad04d909610cecb01d5a4ba2c99cb997f3/college-majors/majors-list.csv'), stringsAsFactors = FALSE)
str(df)
```

```{r using grep}
data_statistics_major =  df$Major[grep("DATA|STATISTICS", df$Major)]
data_statistics_major
```

# 2 Write code that transforms the data below:

[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"

[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  

[9] "elderberry"   "lime"         "lychee"       "mulberry"    

[13] "olive"        "salal berry"

Into a format like this:

c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")

```{r}
fruits_veg <- '[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"

[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  

[9] "elderberry"   "lime"         "lychee"       "mulberry"    

[13] "olive"        "salal berry"'
```

```{r}
fruits_veg
```
```{r}
fruits_veg_wo= unlist(str_extract_all(fruits_veg, pattern = "\"([a-z]+.[a-z]+)\""))
fruits_veg_wo
```

```{r}
fruits_veg_wo_cl= str_remove_all(fruits_veg_wo, "\"")
fruits_veg_wo_cl=c(fruits_veg_wo_cl)
fruits_veg_wo_cl
```

The two exercises below are taken from R for Data Science, 14.3.5.1 in the on-line version:

#3 Describe, in words, what these expressions will match:

```{r}
words <- '[1] "bell pepper"  "bilberry"     "church"   "pressure"

[5] "blueberry"    "eleven"   "chili pepper" "apple"  

[9] "abcdfdfbcafgfdg"   "papaya"         "dad"       "mulberry"    

[13] "believe"        "salal berry" "Banana"  "coconut"'

words_wo= unlist(str_extract_all(words, pattern = "\"([a-z]+.[a-z]+)\""))
wrods_wo_cl= str_remove_all(words_wo, "\"")
```


(.)\1\1

Match any strings that have a character that repeats back to back

```{r}
expression1 = "(.)\1\1"
wrods_wo_cl %>% 
  str_subset(expression1)
```

"(.)(.)\\2\\1"

This could match anything like 4 characters, with the first and last matching and then the two middle matching.

```{r,}
expression2 = "(.)(.)\\2\\1"
wrods_wo_cl %>% 
  str_subset(expression2)
```

(..)\1

String contains the exact same character, repeated 2 or more times

```{r}
expression3 = "(..)\1"
wrods_wo_cl %>% 
  str_subset(expression3)
```

"(.).\\1.\\1"

it will look for 3 repeating words in a string.

```{r}
expression4 = "(.).\\1.\\1"
wrods_wo_cl %>% 
  str_subset(expression4)
```

"(.)(.)(.).*\\3\\2\\1"

it will look at the first three letters and then see if there is an opposite pattern like abcdfdfdfcba.

```{r}
expression5 = "(.)(.)(.).*\\3\\2\\1"
wrods_wo_cl %>% 
  str_subset(expression5)
```

#4 Construct regular expressions to match words that:

Start and end with the same character.
```{r}
expression9 = "^(.).*\\1$"
wrods_wo_cl %>% 
  str_subset(expression9)
```
Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)
```{r}
expression6 = "(..).*\\1"
wrods_wo_cl %>% 
  str_subset(expression6)
```

Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)
```{r}
expression7 = "(.).*\\1.*\\1"
wrods_wo_cl %>% 
  str_subset(expression7)
```