---
title: "HW11"
author: "Shariq Mian"
date: "2023-05-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
head(cars)
```

Plot Data
In this linear model, speed is the independent variable and stopping distance is the dependent variable.

The plot shows that stopping distance increases as speed increases.

```{r}
plot(cars, xlab = "Speed", ylab = "Stopping distance")
```

Linear Model
This linear model is based on a single factor regression. speed is the independent variable (input) and stopping distance is the dependent variable (output).

The intercept is -17.5791. The slope is 3.9324.

The one factor linear model is:

stopping distance = -17.5791 + 3.9324 * speed
```{r}
cars.lm <- lm(dist ~ speed, data = cars)
summary(cars.lm)
```

Linear Model Summary
Upon analyzing the linear model, the residuals distribution suggests a normal distribution, indicating a good fit.

The standard error for the speed coefficient is approximately 9.4 times the coefficient value, indicating a relatively low variability. This aligns with the expectation of a good model, where the standard error should be significantly smaller than the coefficient.

The p-value of 1.49e-12 suggests that the speed coefficient is highly significant and relevant in predicting the stopping distance. This means that the speed variable plays a crucial role in the model.

The intercept also holds significance in the model, as indicated by its p-value of 0.0123.

The multiple R-squared value of 0.6511 implies that the model explains approximately 65.11% of the variation in the data. This demonstrates a moderate to strong level of explanatory power.

```{r}
#Plot of Linear Model
plot(cars, xlab = "Speed", ylab = "Stopping distance")
abline(cars.lm)
```


Plot the Risiduals

The plot below shows that the residuals look uniformly distributed around zero. The residuals appear to be uniformly scattered above and below zero.
```{r}
plot(fitted(cars.lm), resid(cars.lm))
```

Normal Q-Q Plot
The plot below suggests that there’s some skew to the right.
```{r}
qqnorm(resid(cars.lm))
qqline(resid(cars.lm))
```


