---
title: "HW12"
author: "Shariq Mian"
date: "2023-05-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
url <- 'https://github.com/mianshariq/SPS/raw/15791aaf54198f05264e55d1bce0efba5ef550b1/Data%20605/who.csv'
who <- read.csv(url)
head(who)
```


## 1
Provide a scatterplot of LifeExp~TotExp, and run simple linear regression. Do not transform the variables. Provide and interpret the F statistics, R^2, standard error,and p-values only. Discuss whether the assumptions of simple linear regression met.

```{r}
plot(who$TotExp, who$LifeExp, xlab = "Total Expenditures", ylab = "Life Expectancy")
```


```{r}
who_simple.lm <- lm(LifeExp ~ TotExp, data = who)
```

## Summary Statistics
```{r}
summary(who_simple.lm)
```


The F-table value for 1 regression degree of freedom and 120 residual degrees of freedom is 6.851. 
Since the F-statistic from our model, which has 1 regression degree of freedom and 188 residual
degrees of freedom, is 65.26, is much greater than the F-table value, the F-statistic suggests we 
can reject the null hypothesis (a regression model with a zero coefficient). Similarly, the p-value 
is well below typical α thresholds. The R2=0.2577 value is not strong, it tells us that 25.77% of 
the variation in the data is accounted for in our model, which means the model does not strongly 
fit the data. The standard error is a reasonably small percentage of the coefficient.

## 2
Raise life expectancy to the 4.6 power (i.e., LifeExp^4.6). Raise total expenditures to the 0.06 power (nearly a log transform, TotExp^.06). Plot LifeExp^4.6 as a function of TotExp^.06, and r re-run the simple regression model using the transformed variables. Provide and interpret the F statistics, R^2, standard error, and p-values. Which model is “better?”
```{r}
who$LifeExp4.6 <- (who$LifeExp)^4.6
who$TotExp0.06 <- (who$TotExp)^0.06
plot(who$TotExp0.06, who$LifeExp4.6, xlab = "Total Expenditures ^ 0.06", ylab = "Life Expectancy ^ 4.6")
```

# Run simple linear regression
```{r}
who_transformed.lm <- lm(LifeExp4.6 ~ TotExp0.06, data = who)
summary(who_transformed.lm)
```

The F-statistic from our transformed model is 507.7 (same degrees of freedom as model from 1.)
is much better vs. the F-table value than the prior model. Similarly, the p-value is even
better. Finally, the R2=0.7298 value is dramatically superior to our model from 1. The 
transformed model is the better model. The standard error is a reasonably small percentage of 
the coefficient.
## 3. 
Using the results from 3, forecast life expectancy when TotExp^.06 =1.5. Then forecast life expectancy when TotExp^.06=2.5.

Our model is LifeExp4.6=−736527910+620060216∗TotExp0.06

```{r}
le.transformed <- function(totexp) {
  return((-736527910 + (620060216 * totexp))^(1/4.6))
}

# Example usage
result1 <- le.transformed(1.5)
result2 <- le.transformed(2.5)

result1
result2

```

## 4. 
Build the following multiple regression model and interpret the F Statistics, R^2, standard error, and p-values. How good is the model? LifeExp = b0+b1 x PropMd + b2 x TotExp +b3 x PropMD x TotExp

```{r}
who_multiple.lm <- lm(who$LifeExp4.6 ~ who$PropMD + who$TotExp0.06 + who$PropMD:who$TotExp0.06)
summary(who_multiple.lm)
```
The F-statistic from our multiple regression model is 180.3 which is well above the 
F-table value of 3.949 for 3 regression degrees of freedom and 120 residual degrees of 
freedom and α=0.01. Similarly, the p-value is strong for the model, and strong for all of 
the variables except PropMD x TotExp0.06, which is still pretty good (0.0622). Finally, the 
R2=0.7441 value is quite good. The standard error values for PropMD and PropMD x TotExp
could be better.

##5. 
Forecast LifeExp when PropMD=.03 and TotExp = 14. Does this forecast seem realistic? Why or why not?
Our model is LifeExp4.6=−724418697+(47273338389∗PropMD)+(604795792∗TotExp0.06)−(21214671638∗PropMD∗TotExp0.06)

```{r}
le.transformed_mutiple <- function(propmd, totexp) {
  (-724418697 + (47273338389 * propmd) + (604795792 * totexp) - (21214671638 * propmd * totexp))^(1/4.6)
}
pmd <- 0.03
te <- 14
te4.6 <- te^0.06
le.transformed_mutiple(pmd, te4.6)
```

The PropMD ratio being used for the prediction is only in-line with a few outlying data 
points. If we plot PropMD against Life Expectancy, we can see the overwhelming majority
of data points are between 0.000 and 0.005. Then we see two major outlier data points around
0.325 and 0,035. I always get nervous when predicting values that are not in the range of the 
values for an overwhelming percentage of observations. The Total Expenditure is also towards
the bottom end of the range, though a lot of values exist in that range.
plot(who$PropMD, who$LifeExp, xlab = "Proportion MDs", ylab = "Life Expectancy")
