---
title: "HW13"
author: "Shariq Mian"
date: "2023-05-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Calculus with R
1. Use integration by substitution to solve the integral below.

u=−7xdu=−7dx
∫4e−7xdx
∫−47eudu
∫−47eudu
−47∫eudu
−47eu+C
−47e−7x+C


2. Biologists are treating a pond contaminated with bacteria. The level of contamination is changing at a rate of dNdt=−3150t4−220
 bacteria per cubic centimeter per day, where t is the number of days since treatment began. Find a function N(t) to estimate the level of contamination if the level after 1 day was 6530 bacteria per cubic centimeter.


dNdt=−3150t4−220

3150∫1t4dt−220∫1dt

3150∫−13t3−220t

\bigg\frac{1050}{t^3}-220t+C

N(1)=1050t3−220t+C

6530=105013−220(1)+C

6530=1050−220+C

5700=C

N(t)=1050t3−220t+5700



3. Find the total area of the red rectangles in the figure below, where the equation of the line is f(x)=2x−9
 [4.5,8.5].
```{r}
f <- function(x) 2*x-9
paste0('The area is ',integrate(f,4.5,8.5)$value)
```
## [1] "The area is 16"
4. Find the area of the region bounded by the graphs of the given equations.
y = x2−2x−2
, y=x+2

Bounds: x2−2x−2=x+2
 x2−3x−4=0
 (x−4)(x+1)=0
 x={4,−1}
```{r}
y_one <- function(x) x+2
y_two <- function(x) x^2 - 2*x -2

int_one <- integrate(y_one,-1,4)
int_two <- integrate(y_two,-1,4)
total_area <- int_one$value - int_two$value
```
## [1] "The area of the region bounded by interval [-1,4] is: 20.833"


5. A beauty supply store expects to sell 110 flat irons during the next year. It costs $3.75 to store one flat iron for one year. There is a fixed cost of $8.25 for each order. Find the lot size and the number of orders per year that will minimize inventory costs.


assumption: 2 flat irons stored on average x=flat iron orders c = cost function storagecosts=3.75∗x/2=1.875x
  ordercosts=8.25∗110/x=907.5/x

costfunction=1.875x+907.5/x

c′(x)=1.875−907.5x2

c′(x)=1.875x2=907.5

x2=907.51.875

x=(√907.51.875)

x=22

c=1.875∗22+907.5/22=$82.5

lotsize=110/x=5



6. Use integration by parts to solve the integral below.


∫ln(9x)∗x6dx

d(uv)=udv+vdu

∫d(uv)=uv=∫udv+∫vdu

∫udv=uv−∫vdu

u=ln(9x)

dvdx=x6

du=99xdx=1xdx

dv=x6dx

v=17x7

ln(9x)17x7−∫17x71xdx

ln(9x)x77−x749−C

x7(7ln(9x)−1)49+C


7. Determine whether f ( x ) is a probability density function on the interval 1, e 6 . If not, determine the value of the definite integral.f(x)=16x
```
f_sev <- function(x) 1/(6*x)
is_pdf <- integrate(f_sev,1,exp(6))
```
## [1] "Since the integral equals 1 from 1 to e^6 it is a probability density function."