---
title: "Data605_HW3"
author: "Shariq Mian"
date: "03/05/2023"
output:
  pdf_document:
    toc: yes
  html_document:
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries}
library(pracma)
```

# Problem Set 1

### Q1 What is the rank of the matrix A?

```{r}
A = matrix(c(1,2,3,4,-1,0,1,3,0,1,-2,1,5,4,-2,-3), nrow=4, byrow=TRUE)
A
rref(A)
```

Ans: Here we count the number of non zero linearly independent vectors rows, which is equal to 4.

### Q2 Given an mxn matrix where m > n, what can be the maximum rank? The minimum rank, assuming that the matrix is non-zero?

Ans: 
If the matrix has (M > N), meaning rows than columns, the maximum rank is N.
For minimum rank, since the matrix is non-zero, the rank is at least 1.

### Q3 What is the rank of matrix B?
```{r}
B = matrix(c(1,2,1,3,6,3,2,4,2), nrow=3, byrow=TRUE)
B
rref(B)
```

There is one (1) non-zero row, therefore the rank is 1. 


# Problem Set 2

### Q 
Compute the eigenvalues and eigenvectors of the matrix A. 

```{r}
C <- matrix(c(1,2,3,0,4,5,0,0,6), nrow=3, byrow=TRUE)
C
```

