---
title: "HW7"
author: "Shariq Mian"
date: "5/11/2023"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Question 1.
1. Let X1, X2, . . . , Xn be n mutually independent random variables, each of
which is uniformly distributed on the integers from 1 to k. Let Y denote the
minimum of the Xi’s. Find the distribution of Y.

y= 1≤j≤k, ((k−j+1)**n−(k−j)**n)/kn

Question 2
2. Your organization owns a copier (future lawyers, etc.) or MRI (future doctors).This machine has a manufacturer’s expected ### lifetime of 10 years. This means that we expect one failure every ten years. (Include the probability statements and R Code for each part).
```
P(One failure in ten years)=1/10

P(No failures in ten years)=9/10
```
a. What is the probability that the machine will fail after 8 years?. Provide also the
expected value and standard deviation. Model as a geometric. (Hint: the probability is
equivalent to not failing during the first 8 years.)


```{r}
p = 1/10
q = 9/10
n=8

year = 9
v = vector()
for (k in 1:year) {
 v[k] = p*(q^(k-1))
 
}

prob_ofeight =round(pgeom(n,p,lower.tail = F),3)

E_x = 1/p

sig = round(sqrt(1-p)/p,3)

prob_ofeight
E_x
sig

```

b. What is the probability that the machine will fail after 8 years?. Provide also the
expected value and standard deviation. Model as an exponential.

```{r}
lam = 1/10

expo = round(exp(-n/10),3)
rprob=round(pexp(p,n,lower.tail = F),3)

gE_x = 1/lam

var = 1/lam^2

std = 1/lam
gE_x
var
std
```

c. What is the probability that the machine will fail after 8 years?. Provide also the
expected value and standard deviation. Model as a binomial. (Hint: 0 success in 8 years)

```{r}
pbin<- round(pbinom(q,n,p),3)

bex <- round(n*p,3)

b_stdx <- sqrt(n*p*q)

bex
b_stdx 
```


d. What is the probability that the machine will fail after 8 years?. Provide also the
expected value and standard deviation. Model as a Poisson.


```{r}
plamb <- n*p
pe_x <- plamb

p_prob =round(ppois(q,plamb),3)
p_std = round(sqrt(plamb),3)

p_prob
p_std