---
title: "Project1"
author: "Shariq Mian"
date: "9/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Libraries

## Importing Libraries

```{r, warning=FALSE}
library(stringr)
library(DT)
library(ggplot2)
library(tidyverse)
```

# Loading
Reading the text file from Github

```{r}
df = readr::read_lines('https://github.com/mianshariq/SPS/raw/0ac39799e67b32b6c75564847778f012ffa5faa4/Data%20607/Projects/Project%201/ratings.txt')
```

#  Cleaning
Removing the dashes and empty rows and first two lines
```{r}
df1 = str_remove_all(string = df, pattern = "^-+$")     #remove the dashes
df1 = df1[sapply(df1, nchar) > 0]                     # remove the empty rows
df1 = df1[-c(0:2)]                                    # remove the first two lines headers
```
Spliting data into even odd so I can contcat into one row.
```{r}
df1_odd <- df1[seq(1, 128, 2)]
df1_even <- df1[seq(2, 128, 2)]
```

Concat and remove slashes from data
```{r}
df2 = paste(df1_odd, df1_even, sep = " ")
df2 = str_replace_all(string = df2, pattern = "/", "|")
```

Using Regex for string minupulation and extraction
```{r, warning=FALSE}
name = str_extract(df2, "[[:alpha:]]{2,}([[:blank:]][[:alpha:]]{1,}){1,}")
head(name,3)
states = str_extract(df1_even, "[[:alpha:]]{2}")
head(states,3)
points = str_extract(df2, "[[:digit:]]+\\.[[:digit:]]")
points = as.numeric(as.character(points))
head(points,3)
pre_ratings = str_extract(df2, ".\\: \\s?[[:digit:]]{3,4}")
pre_ratings = as.numeric(str_extract(pre_ratings, "\\(?[0-9,.]+\\)?"))
id <- as.integer(str_extract(df2, "\\d+"))
id<-subset(c(id),c(id)<65)
head(id,3)
opp_num<-str_extract_all(str_extract_all(df2,"\\d+\\|"),"\\d+")
opp_num<-subset(c(opp_num),c(opp_num)!="0")
opp_num[1]
```

Using loop to get the average of the opponnent.
```{r}
OppAvgRating <- list()

for (i in 1:length(opp_num)){
  OppAvgRating[i]<- mean(pre_ratings[as.numeric(unlist(opp_num[id[i]]))])
  }

opp_avg <- lapply(OppAvgRating, as.numeric)
opp_avg <- lapply(OppAvgRating, as.numeric)
opp_avg <- data.frame(unlist(opp_avg))
opp_avg = round(opp_avg)
opp_avg
```

# Creating Data Frame
Creating DF of the 5 columns needed.
```{r}
df3=data.frame(name,states,points,pre_ratings,opp_avg)
datatable(df3, extensions = 'Scroller', options = list(scrollY = 500, scroller = TRUE ))
```

# Visualization
Creating plot of states. 
```{r}
ggplot()+
  geom_bar(data = df3, aes(states))+
  coord_flip()
```

Creating bins for ratings to get a better view of the ratings as a group.
```{r}
df3$ratingbins=cut(df3$pre_ratings, 15, include.lowest=TRUE, dig.lab = 4)
ggplot()+
geom_bar(data = df3, aes(ratingbins))+
coord_flip()
```

Creating plot of ratings vs avg opponent ratings, you can see if you average opponent is great and you have many points, that means your ratings is high
```{r, fig.width=15}
ggplot(df3, aes(pre_ratings, unlist.opp_avg., color = ratingbins)) +
geom_point(aes(size = points))+
ggtitle('Pre-rating Vs. Avg Opponent Rating')+
xlab('Pre-rating')+
ylab('unlist.opp_avg')
```
Displaying the data
```{r}
head(df3)
```
```{r}
#Calculating expected score for the players
df3$elo_score<- (1 / (1 + 10^((df3$pre_ratings - df3$unlist.opp_avg.)/400)))
# Assuming The rating of player is updated using the formula rating1 = rating1 + K*(Actual Score – Expected score_ where 'k' weighting factor is assumed as '20'
df3$elo_pts <-  df3$pre_ratings  + 20*(1-df3$elo_score)

#to compare with final score, let's fetch it from raw data

df3$diff <- df3$pre_ratings - df3$elo_pts
df3



```

# Extracting CSV
```{r}
write.csv(df3, "elo_chess.csv", row.names = FALSE)
```
