---
title: "TidyVerse CREATE"
author: "Shariq Mian"
date: "10/24/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Your task here is to Create an Example. Using one or more TidyVerse packages, and any dataset from fivethirtyeight.com or Kaggle, create a programming sample “vignette” that demonstrates how to use one or more of the capabilities of the selected TidyVerse package with your selected dataset. (25 points)

Later, you’ll be asked to extend an existing vignette. Using one of your classmate’s examples (as created above), you’ll then extend his or her example with additional annotated code. (15 points)

You should clone the provided repository. Once you have code to submit, you should make a pull request on the shared repository. You should also update the README.md file with your example.

After you’ve created your vignette, please submit your GitHub handle name in the submission link provided below. This will let your instructor know that your work is ready to be peer-graded.

You should complete your submission on the schedule stated in the course syllabus.


```{r Libraries}
library(dplyr)
library(reactable)
```

```{r read}
df<- read.csv('https://github.com/mianshariq/SPS/raw/db42e306e0eb9cc8d92bc5dc2cc65ddff0db0799/Data%20607/Projects/TidyVerse/historical_RAPTOR_by_team.csv')
```


```{r}
glimpse(df)
```

```{r}
df %>% select(player_name,war_total)
```
```{r}
df_1= df %>% 
  filter(player_name == 'Michael Jordan')
df_1
```



```{r}
df %>% 
  top_n(10, war_total)
```

# Ranking all time total War

```{r}
df1 <- df %>% 
  select(player_name, season, team, poss, war_total) %>% 
  group_by(player_name) %>% 
  summarise(warss_totals = sum(war_total)) %>% 
  arrange(desc(warss_totals))
df1
```


```{r}
df %>% 
  mutate(war_per_mp = (war_total / poss)) %>% 
  arrange(desc(war_per_mp))
```
